Learning Excursion Sets of Vector-valued Gaussian Random Fields for Autonomous Ocean Sampling

### 2020-07-01 main_new.tex
updates

The case study considers the upper water column in the river plume,
represented by a two dimensional grid. Extensions to three-dimensional
domains are not methodologically different, but likely approximate
calculations by concentrating numerical integration on terms in the
vicinity of the autonomous vehicle \citep{fossum18b}. While we did not
consider any temporal effects, which would be relevant on a larger
time scale, we do consider the extension to spatio-temporal modeling
and envision that advection-diffusion equations could be useful \citep{sigrist2015stochastic,richardson2017sparsity}. For more complex
oceanographic phenomena, the methods will need to be extended to
non-Gaussian phenomena, possibly feature-based mixtures of Gaussian
processes which could still be run onboard and augmented by dynamical
models. Running large numerical models onboard a robotic vehicle is not currently possible, but high-resolution ocean model or satellite data can be used to fit a more complex statistical model.

@@

TOF acknowledges support from the Centre for Autonomous Marine
Operations and Systems (AMOS), Center of Excellence, project number
223254, and the Applied Underwater Robotics Labortatory (AURLab). CT
and DG acknowledge support from the Swiss National Science Foundation,
project number 178858. JE and KR acknowledge support from Norwegian
research council (RCN), project number 305445. DG would like to
aknowledge support of Idiap Research Institute, his primary affiliation in an early version of this manuscript. The authors would also like to thank Niklas Linde of the University of Lausanne for providing constructive feedback about this work, and finally members of the AURLab for help with AUV deployments

>>>>

The case study considers the upper water column in the river plume,
represented by a two dimensional grid. Extensions to three-dimensional
domains are not methodologically different, but likely approximate
calculations by concentrating numerical integration on terms in the
vicinity of the autonomous vehicle \citep{fossum18b}. While we did not
consider any temporal effects, which would be relevant on a larger
time scale, we do consider the extension to spatio-temporal modeling
and envision that advection-diffusion equations could be useful
\citep{sigrist2015stochastic,richardson2017sparsity}. For more complex
oceanographic phenomena, the methods will need to be extended to
non-Gaussian phenomena, possibly feature-based mixtures of Gaussian
processes which could potentially be run onboard augmented by
dynamical models. Running numerical models onboard a robotic vehicle
is currently infeasible, but high-resolution ocean models or remote
sensing data can be used to fit a more complex statistical model
\cite{davidson19}.

@@

TOF acknowledges support from the Centre for Autonomous Marine
Operations and Systems (AMOS), Center of Excellence, project number
223254, and the Applied Underwater Robotics Labortatory (AURLab). CT
and DG acknowledge support from the Swiss National Science Foundation,
project number 178858. JE and KR acknowledge support from Norwegian
research council (RCN), project number 305445. DG would like to
aknowledge support of Idiap Research Institute, his primary
affiliation in an early version of this manuscript. The authors would
also like to thank Niklas Linde of the University of Lausanne for
providing constructive feedback about this work, and members of the
NTNU AURLab for help with AUV deployments
